### 2020-11-12 doc/manuscript/Dow_manuscript.Rmd
study sites

Study sites included **2/3** temperate forests in the Eastern United states, **both/all** part of the Forest Global Earth Observatory [ForestGEO; Anderson-Teixeira et al. 2015] (**Table 1?**). **Both/all** sites are dominated by broadleaf deciduous trees. *(insert site descriptions, including lat/long, elevation, plot size, climate info, dominant species. If we include SERC and if space permits, we may put this in a table, otherwise just text)*

Our first study site was the forest dynamics plot located at the Smithsonian COnservation Biology Institute 5 KM South of Front Royal, Virginia within the Blue Ridge Mountains (38 °53036.6″ N, 78°08043.4″W; elevation 273–338 m). The forest here was established in the mid-19th century after conversion from agricultural fields. Dominate canopy species within the 25.6 HA forest plot include tulip poplar (Liriodendron tulipifera), hickories (Carya spp.), and oaks (Quercus spp.). The climate is humid temperate, with a mean annual precipitation of 998 mm, January temperatures averaging 1 degrees C and July temperatures averaging 24 degrees C (Helcoski et al, 2019).

The second study site was Harvard Forest in the central Massachusetts town of Petersham (42°53′ N, 72°17′ W, elevation?). Harvard forest was established in 1907 as a study site for university students and researchers. (Previous use?) Dominate species within the approximately 13 HA plot are hemlock (Tsuga spp.), oak (Quercus spp.) and maple (Acer spp.). The climate is temperate continental with a mean annual precipitation of 1120 mm, January temperatures averaging -12 degrees C and July temperatures averaging 19 degrees C (D'Orangeville et al, ).

The third study site was the forest dynamics plot located at the Smithsonian Ecological Research Center in Edgewater, Maryland near a sub estuary of the Chesapeake Bay (38°88′ N, 76°55′ W, elevation?). The forest here established roughly 120 years ago, while the plot was established in 2007. The 16 HA plot is dominated by tulip poplar (Liriodendron tulipifera), oak (Quercus spp.), beech (Fagus spp.), hickory (Carya spp.), and maple (Acer spp.). (Climate summary)

>>>>

Study sites included two temperate forests in the Eastern United States, both part of the Forest Global Earth Observatory [ForestGEO; Anderson-Teixeira et al. 2015].

Our first study site was the forest dynamics plot located at the Smithsonian Conservation Biology Institute 5 km South of Front Royal, Virginia within the Blue Ridge Mountains (38.8935° N, -78.1454° W; elevation 273–338 m.a.s.l.). The forest here was established in the mid-19th century after conversion from agricultural fields. Dominate canopy species within the 25.6 HA forest plot include tulip poplar (*Liriodendron tulipifera*), oaks (*Quercus spp.*), hickories (*Carya spp.*). The climate is humid temperate, with a mean annual precipitation of 998 mm, January temperatures averaging 1 degrees C and July temperatures averaging 24 degrees C (Helcoski et al, 2019).

The second study site was Harvard Forest (42.5388° N, 72.1755° W, 340-368 m.a.s.l.), located near the central Massachusetts town of Petersham. *Harvard Forest was established in 1907 as a study site for university students and researchers. (Previous use?)* Dominate species within the approximately 13 HA plot are hemlock (*Tsuga spp.*), oak (*Quercus spp.*) and maple (*Acer spp.*). The climate is temperate continental with a mean annual precipitation of 1120 mm, January temperatures averaging -12 degrees C and July temperatures averaging 19 degrees C (D'Orangeville et al, ).
